---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(labzenr)
notebook_py <- system.file("extdata", "dummylab.ipynb", package = "labzenr")
```

## Function - extract_points()

```{r}

total_points  <- extract_points(notebook_py)
total_points
```

The output dataframe is a section-by-section overview of points available in the lab assignment.

## Function - count_points()

```{r}
extracted_points  <- count_points(notebook_py)
extracted_points
```

The output dataframe is a cross table summarising the number of optional, required, and total points per lab.


## Function - check_mechanics()

```{r}
check_mechanics()
```

This function performs the following tests on your current git repository:

* Check that you have included a Github repo link;
* Check that you have pushed the latest version; and
* Check that you have at least three commits.

